---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[phenoptr]: https://perkinelmer.github.io/phenoptr/

# phenoptrExtra

The goal of phenoptrExtra is to extend the [phenoptr] package with additional functionality for working with immunofluorescence data tables exported from the PerkinElmer inForm software.

## Installation

You can install the unreleased development version of phenoptrExtra from GitHub with:

``` r
devtools::install_github("gerkelab/phenoptrExtra")
```

## This Package is in the Development Stage

```{r}
library(phenoptrExtra)
```

### What works now

```{r echo=FALSE}
print_description <- function(function_name) {
  capture.output(
    tools::Rd2txt(paste0("man/", function_name, ".Rd"), 
                  options = list(underline_titles = FALSE))
  ) %>% 
    .[grep("Description", .):(grep("Usage", .) - 3) + 2] %>% 
    stringr::str_trim()
}

print_examples <- function(function_name) {
  capture.output(
    tools::Rd2txt(paste0("man/", function_name, ".Rd"), 
                  options = list(underline_titles = FALSE))
  ) %>% 
    .[(grep("Examples", .) + 2):length(.)] %>% 
    .[!grepl("Not run", .)] %>% 
    stringr::str_trim() %>% 
    .[. != ""]
}
```

#### Importing

```r
import_all_csd()
```

```{r echo=FALSE, results="asis"}
cat(">", print_description("import_all_csd"))
```

```{r echo=FALSE, results="asis"}
cat(paste("    ex>", print_examples("import_all_csd"), collapse = "\n"))
```

#### Tidying and Preparing

```r
merge_sample_info()
```

```{r echo=FALSE, results="asis"}
cat(">", print_description("merge_sample_info"))
```

```{r echo=FALSE, results="asis"}
cat(paste("    ex>", print_examples("merge_sample_info"), collapse = "\n"))
```

```r
reorder_phenotype()
```

```{r echo=FALSE, results="asis"}
cat(">", print_description("reorder_phenotype"))
```

```{r echo=FALSE, results="asis"}
cat(paste("    ex>", print_examples("reorder_phenotype"), collapse = "\n"))
```

#### Counting Cell Types

```r
count_observations()
count_cells()
```

```{r echo=FALSE, results="asis"}
cat(">", print_description("count_observations"))
```

```{r echo=FALSE, results="asis"}
cat(paste("    ex>", print_examples("count_observations"), collapse = "\n"))
```

#### Working with IF Intensity

```r
gather_cell_intensity()
```

```{r echo=FALSE, results="asis"}
cat(">", print_description("gather_cell_intensity"))
```

```{r echo=FALSE, results="asis"}
#cat(paste("    ex>", print_examples("gather_cell_intensity"), collapse = "\n"))
```

```r
choose_measure()
```

```{r echo=FALSE, results="asis"}
cat(">", print_description("choose_measure"))
```

```{r echo=FALSE, results="asis"}
#cat(paste("    ex>", print_examples("choose_measure"), collapse = "\n"))
```

```r
csd %>% 
  group_by(Sample) %>% 
  gather_cell_intensity(
    `CD3`   = choose_measure("Membrane",    520, "Mean"), 
    `CD8`   = choose_measure("Membrane",    540, "Mean"),
    `FOXP3` = choose_measure("Entire Cell", 570, "Mean"),
    `PD1`   = choose_measure("Membrane",    620, "Mean"),
    `PD-L1` = choose_measure("Entire Cell", 650, "Mean"),
    `PCK`   = choose_measure("Entire Cell", 690, "Mean")
  )
```
